Staged Abstract Interpreters

### 2019-02-19 paper/10_intro.tex
misc

Besides the intellectual merit of the confluence diagram, this paper contributes
to a practical problem in static analysis: can we speed up a static analyzer
without any intrusive changes and soundness compromises?
\todo{specializing analysis wrt program is not new; first staging; we argue that
staging is less intrusive compared with AC (ie, closure generation), in
fact,LMS-based staging only requires type annotations }

>>>>

Besides the intellectual merit of the confluence diagram, this paper contributes
to a practical problem in static analysis: can we speed up a static analyzer
without any intrusive changes and soundness compromises?
\todo{specializing analysis wrt program is not new; first staging; we argue that
staging is less intrusive compared with AC (ie, closure generation), in
fact,LMS-based staging only requires type annotations, static analysis trade-off
between precision and efficiency, we argue that mp is an approach to improve the
latter one while fix the former one}

### 2019-02-19 paper/70_related.tex
revise
some moands
misc

\citet{damian1999partial} provides a formal treatment to abstract compilation
and Shiver's CFA, as well as proofs to establish correctness and certified
specialized analyzers \cite{damian1999partial}. \citeauthor{amtoft1999partial}
applyies partial evaluation for constraint-based control flow analysis
\cite{amtoft1999partial}. Split the analysis to be multiple stages is also
studied other than control-flow analysis, though the formulation may very
different. For example, \citeauthor{DBLP:conf/cgo/HardekopfL11} apply staging to
flow-sensitive pointer analysis \cite{DBLP:conf/cgo/HardekopfL11}. The first
stage is to analyze the program code to obtain a sparse representation, and then
the second stage conducts the flow-sensitive analysis.

\citeauthor{DBLP:conf/popl/SinghPV17} optimizes polyhedra abstract domain
through online decomposition \cite{DBLP:conf/popl/SinghPV17,
Singh:2017:PCD:3177123.3158143}. The idea is to decompose a large polyhedra into
several smaller one; one abstract transformer usually only depends a limit
number of variables, then we just need to compute the resulting polyhera on
those smaller polyhedra that contains these related variables. The decomposition
can be considered as a specialization of abstract domain with respect to the
program static structure.

\paragraph{Abstract Interpreters} Abstract interpretation was proposed as a
semantic-based approach to construct sound static analysis by approximation
\cite{DBLP:conf/popl/CousotC77}. As semantic artifacts, the Abstracting Abstract
Machines (AAM) \cite{DBLP:journals/jfp/HornM12, DBLP:conf/icfp/HornM10} approach
shows that abstract interpreters can be derived systematically from concrete
semantic artifacts. The big-step abstract interpreters we presented in this
paper are also inspired by the AAM framework, which are later adopted for
big-step abstract interpreters \cite{DBLP:journals/pacmpl/DaraisLNH17,
Wei:2018:RAA:3243631.3236800}. \citet{DBLP:conf/cc/CousotC02} also proposed an
abstract interpretation framework for modular analysis.
\citet{DBLP:conf/popl/CalcagnoDOY09} developed compositional shape analysis by
using bi-abduction. The big-step abstract interpreter we presented in this paper
is inspired by \cite{DBLP:journals/pacmpl/DaraisLNH17,
Wei:2018:RAA:3243631.3236800}. \citet{Keidel:2018:CSP:3243631.3236767}
demonstrate a similar implementation of definitional abstract interpreter using
arrows.

@@

>>>>

\citet{damian1999partial} provides a formal treatment to abstract compilation
and Shiver's CFA, as well as proofs to establish correctness of the certified
specialized analyzer \cite{damian1999partial}. \citeauthor{amtoft1999partial}
applied partial evaluation for constraint-based control flow analysis
\cite{amtoft1999partial}. Splitting an analysis into multiple stages is also
studied for analysis other than for control-flow, though the formulation may very
different. For example, \citeauthor{DBLP:conf/cgo/HardekopfL11} apply staging to
flow-sensitive pointer analysis \cite{DBLP:conf/cgo/HardekopfL11}. The first
stage is to analyze the program code to obtain a sparse representation, and then
the second stage conducts the flow-sensitive analysis based on the first one.

\citeauthor{DBLP:conf/popl/SinghPV17} optimizes polyhedra abstract domains
through online decomposition \cite{DBLP:conf/popl/SinghPV17,
Singh:2017:PCD:3177123.3158143}. The idea is to decompose a large polyhedra into
several smaller one; one abstract transformer usually only depends a limit
number of variables, then we just need to compute the resulting polyhera on
those smaller polyhedras which contain these related variables. The decomposition
can be considered as a specialization of abstract domain with respect to the
static program structure.

\paragraph{Abstract Interpreters} Abstract interpretation was proposed as a
semantic-based approach to construct sound static analysis by approximation
\cite{DBLP:conf/popl/CousotC77}. As semantic artifacts, the Abstracting Abstract
Machines (AAM) \cite{DBLP:journals/jfp/HornM12, DBLP:conf/icfp/HornM10} approach
shows that abstract interpreters can be derived systematically from concrete
semantic artifacts. The big-step abstract interpreters we presented in this
paper are also inspired by the AAM framework, which are later adopted for
big-step abstract interpreters \cite{DBLP:journals/pacmpl/DaraisLNH17,
Wei:2018:RAA:3243631.3236800}. \cite{DBLP:conf/cc/CousotC02} also proposed an
abstract interpretation framework for modular analysis.
\citet{DBLP:conf/popl/CalcagnoDOY09} developed compositional shape analysis by
using bi-abduction. The big-step abstract interpreter we presented in this paper
is inspired by \cite{DBLP:journals/pacmpl/DaraisLNH17,
Wei:2018:RAA:3243631.3236800}. \citet{Keidel:2018:CSP:3243631.3236767}
demonstrate a similar implementation of definitional abstract interpreter using
arrows.

@@

\cite{10.1007/11561347_18}
